---
title: "1_batch_correct_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells"
author: "Ryuta Yokogawa"
date: "04/07/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/Final")
```

## summary
20221117 kojima data,Amander Clark data, vitro PGCLC dataの比較

data: 
cr601_GRCh38p12chrxmv2_20221222 
Hs_in-vitro (NCLCN#261　d6c11, d6c56, d6c86, d6c117)
Hs_in-vivo (AC7w, AC9w, AC10w, YK11w, AC13w, AC16w)


#set up
## load libraries

```{r}
filename<-"1_batch_correct_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells"
```

```{r,message=FALSE,warning=FALSE}
suppressPackageStartupMessages({

library(Matrix) 
library(batchelor)
library(dendextend)
library(scales)
library(Seurat)
library(SeuratWrappers) 
library(tidyverse)
library(gridExtra)
library(ggplot2)
library(ggrepel)
library(dplyr)
library(patchwork)
library(tidyr)
library(scales)
library(reticulate)
library(data.table)
})
set.seed(0)
```

```{r}
use_condaenv(condaenv = "scrublet", required = TRUE) 
packageVersion("Seurat")
```

# Input raw data 
## read raw data

```{r}
vitro <-readRDS("~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/0_sample/0_vitro_c11_56_86_117_10k.rds")
vivo <-readRDS("~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/0_sample/0_vivoACYK_10K.rds")
```

# dataからgermのみ抽出

```{r}
vivo <-subset(vivo,subset=seurat_clusters%in%c("10","14"))
```

# PGCLCとvivoのgermをmerge

```{r}
seurat <- merge(vitro, y = c(vivo))
count <- seurat[["RNA"]]@counts %>% 
  as.matrix()
```

```{r}
data<-seurat[["RNA"]]@counts%>%
  as.matrix() %>% 
  t()
screcode <- reticulate::import(module="screcode.screcode")
recode<-screcode$RECODE()
data_scRECODE <- recode$fit_transform(data)
rownames(data_scRECODE)<-colnames(seurat)
colnames(data_scRECODE)<-rownames(seurat)
```

```{r}
seurat[["RNA"]]@counts<-data_scRECODE %>% 
  t() %>% 
  Matrix(sparse=TRUE)
```

### normalization

normalize; scale.factor =100K for RECODE
```{r}
seurat <- NormalizeData(seurat, normazation.mathod ="LogNormalize", scale.factor=100000)
Idents(seurat)<-seurat$orig.ident
VlnPlot(seurat, features = "nCount_RNA",  pt.size=.1, y.max=100000, sort = c("c11", "c56","c86", "c117", "AC7w", "AC9w", "AC10w", "YK11w", "AC13w", "AC16w")) + theme(legend.position="right")
```

### Find features

```{r}
seurat <- FindVariableFeatures(seurat, selection.method = "vst", nfeatures = 5000)
top10 <- head(VariableFeatures(seurat), 10)  # Identify the 10 most highly variable genes
# plot variable features with and without labels
plot1 <- VariableFeaturePlot(seurat)
LabelPoints(plot = plot1, points = top10, repel = TRUE)
```

```{r}
n.top=5000 #Number of HVGs
max=0 #Limit HVGs whose cluster average expression value is over max in at least one cluster
mean=0
n.cells=5
```

```{r,fig.width=3,fig.height=5}
pdat<-seurat[["RNA"]]@meta.features
pdat$max<-rowSums(seurat[["RNA"]]@data)
pdat$n.cell<-rowSums(seurat[["RNA"]]@data>2)
```

```{r,fig.width=3,fig.height=5}
SNPs_all<-rownames(pdat)[order(pdat$vst.variance.standardized,decreasing = TRUE)]
genes<-intersect(SNPs_all,c(rownames(pdat)[pdat$vst.mean>=mean&pdat$n.cell>=n.cells])) %>% head(n.top)
pdat$HVGs<-rownames(pdat)%in%genes
```

```{r}
ggplot(pdat,aes(x=max))+
  geom_histogram(binwidth = 5)+
  xlim(0,500)
```

```{r}
ggplot(pdat,aes(x=n.cell))+
  geom_histogram(binwidth = 2)+
  xlim(0,30)
```

```{r,fig.width=3,fig.height=5}
ggplot(pdat,aes(x=vst.mean,y=vst.variance.standardized,color=HVGs))+
  geom_point(show.legend = F)+
  scale_x_log10()+
  scale_color_manual(values=c("FALSE"="black","TRUE"="red"))+
  ggtitle(paste0("DEGs (",length(genes),")"))+
  theme_classic(base_size = 15)
```

### Data scaling

```{r}
all.genes <- rownames(seurat)
seurat<- ScaleData(seurat, features = all.genes)
```

### FAST MNN

```{r}
seurat$batch<-factor(seurat$orig.ident,levels=c("c11","c56","c86","c117","AC7w","AC9w","AC10w","YK11w","AC13w","AC16w" ),labels=c("PGCLC","PGCLC","PGCLC","PGCLC","7W","9W","10W","11W","13W","16W"))
seurat<-SplitObject(seurat, split.by = "batch")
seurat<-lapply(seurat, DietSeurat)
seurat<-RunFastMNN(object.list = seurat)
```

### reduciton and clustering

FASTMNNはPCAのかわりなのでここではPCA不要
```{r}
seurat <- FindNeighbors(seurat, dims = 1:50, reduction = "mnn")
seurat <- FindClusters(seurat, resolution = 0.8)#0.4-1.2推奨
seurat <- RunUMAP(seurat, dims = 1:50, reduction = "mnn", seed.use=42)
```

### MNN Visualization {.tabset .tabset-fade}

```{r}
seurat$orig.ident <- factor(x = seurat$orig.ident, levels = c("c11", "c56", "c86", "c117", "AC7w", "AC9w", "AC10w", "YK11w", "AC13w", "AC16w"))
```

### MNN by original.indent & indent

```{r,echo=FALSE,fig.width = 10, fig.height = 5, fig.margin=TRUE}
DimPlot(seurat, reduction = "mnn", group.by = c("orig.ident", "ident"), ncol = 2, label=TRUE, label.size = 4,dims = c(1,2))
```
### UMAP Visualization {.tabset .tabset-fade}
#### original.indent & indent

```{r,echo=FALSE,fig.width = 10, fig.height = 5, fig.margin=TRUE}
DimPlot(seurat, reduction = "umap", group.by = c("orig.ident", "ident"), ncol = 2, label=TRUE, label.size = 4, pt.size=0.5)
```

```{r,echo=FALSE,fig.width = 10, fig.height = 25, fig.margin=TRUE}
DimPlot(seurat, reduction = "umap", split.by = "orig.ident", ncol = 2, label=TRUE, label.size = 4, pt.size=0.5)
```


### Feature Plot{.tabset .tabset-fade}
#### Germ cells

```{r,echo=FALSE,fig.width = 10, fig.height = 10, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("DDX4","DAZL","SYCP3","GPX1"))
```

#### Early GCs

```{r,echo=FALSE,fig.width = 20, fig.height = 15, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("POU5F1","SOX2","NANOG","LIN28A","SALL4","TFAP2C", "SOX15", "SOX17", "PRDM1", "KIT", "PDPN", "TFCP2L1"))
```

#### Leptotene

```{r,echo=FALSE,fig.width = 10, fig.height = 15, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("ZGLP1","STRA8","REC8","ANHX","ASB9","BHMG1"))
```

#### Zygotene

```{r,echo=FALSE,fig.width = 15, fig.height = 15, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("PIWIL2","PIWIL4","TEX14","PRDM9","SPO11","SYCP2", "RAD51", "RAD51AP2"))
```

#### Pachytene

```{r,echo=FALSE,fig.width = 10, fig.height = 15, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("MAEL","TEX15","STK31","SYCP1","DMC1"))
```

#### Diplotene

```{r,echo=FALSE,fig.width = 20, fig.height = 15, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("TP63","ZP3","FIGLA","NOBOX","NLRP5","FOXO3", "GDF9", "WEE2", "ZP4", "KPNA7", "MVP", "JAG1"))
```

#### Granulosa cell

```{r,echo=FALSE,fig.width = 15, fig.height = 15, fig.margin=TRUE}
FeaturePlot(seurat,reduction = "umap",
                  features=c("FOXL2","WT1","CYP17A1","ARX","AMH","INHA", "CYP19A1"))
```

## VlnPlot{.tabset .tabset-fade}

```{r}
markers <- list("Germ cells" =c("DDX4", "DAZL","SYCP3","GPX1"),
                "Early GCs" = c("POU5F1", "SOX2", "NANOG", "LIN28A", "SALL4", "TFAP2C", "SOX15", "SOX17", "PRDM1", "KIT", "PDPN", "TFCP2L1"),
                "Leptotene" = c("ZGLP1", "STRA8", "REC8", "ANHX", "ASB9", "BHMG1"),
                "Zygotene" = c("PIWIL2", "PIWIL4", "TEX14", "PRDM9", "SPO11", "SYCP2", "RAD51", "RAD51AP2"),
                "Pachytene" = c("MAEL", "TEX15", "STK31", "SYCP1", "DMC1" ),
                "Diplotene" = c("TP63", "ZP3", "FIGLA", "NOBOX", "NLRP5", "FOXO3", "GDF9", "WEE2","ZP4", "KPNA7", "MVP", "JAG1"),
                "Fuchou2017" = c("LMOD3", "RBM46", "NETO1", "OOSP2", "BOLL", "SOX13", "TDRD6", "SIX1", "CYP26A1", "CYP26B1", "RDH10", "IL13RA2", "PECAM1", "NANOG", "TFCP2L1", "KLF4", "LMOD3", "RBM46", "NETO1"),
                "Granulosa cell" = c("FOXL2","WT1","CYP17A1","ARX","FOXL2","AMH","INHA","CYP19A1","CYP17A1"),
                "Stromal cell" = c("TCF21","COL1A2","STAR"),
                "smooth muscle cell" = c("DES","ACTA2","CDH5","CALD1","CNN1","HEXIM1","HH2R","H2R","MLNR","GPR38","TAGLN"),
                "endothelial cell" = c("CDH5","VWF","PECAM1","ROBO4"),
                "apoptosis" = c("CASP3","BCL2","BAX","SMAD4"),
                "germ"=c("GATA2","GATA3","ID1","ID2","ID3","MSX1","MSX2","M1AP","HSPB11","SOX2","SOX13","SOX15","SOX17","KIT","KITLG","OOSP2","JAG1","SALL4","DPPA3","TDRD6","PIWIL2","SIX1","TEX12","TEX14","SPO11","WEE2","BOLL","RAD51AP2","RPS19","ZNF208","YBX1","ZNF791","HES6","MAEL","ZNF362","ZBTB11","HOXA5","HOXB6","HMGB3","PBX1","LHX8","NR4A2","ZNF382","MGA","RLF","ZIC4","PAXBP1","HSF2","DMRTA2","L3MBTL1","STAT1","TBX3","AFF1","JARID2", "NFKB2","NR3C2","THRA", "ASB9","ANHX","CYP26A1","CYP26B1","IL13RA2","PECAM1","NANOG","TFCP2L1","KLF4","BMP2","BMP4","GDF2","BMP10","DLL1","DLL4","DLL3","NOTCH1","NOTCH2","NOTCH3","HES1","HEY1","HEY2","HEYL","ACVRL1" ,"ACVR1","BMPR1A","BMPR1B","ACVR1B","ACVR1C","TGFBR1","TGFBR2","BMPR2","ACVR2A","ACVR2B","AMHR2","TGFBR3","TGFBR3L","GAPDH","PPIA","ESR1","ESR2","NR3C1","NR3C2","PGR","AR"),
                "soma"=c("NR5A1","NR2F1","NR2F2","MAF","ESR2","HSD3B1", "HSD17B1","FST","LGR5","SERPINE2","AARD","AKR1C14","GNG13","KRT19","WNT4","RSPO1","KIT","KITLG","WT1","CYP19A1","BMP2", "BMP4","GDF2","BMP10","DLL1","DLL4","DLL3","NOTCH1","NOTCH2","NOTCH3","HES1","HEY1","HEY2","HEYL","ACVRL1","ACVR1","BMPR1A","BMPR1B","ACVR1B","ACVR1C","TGFBR1","TGFBR2","BMPR2","ACVR2A","ACVR2B","AMHR2","TGFBR3","TGFBR3L","GAPDH","PPIA"),
                         "D-BPGs"=c("FOXL2","AARD","HSD17B1","SERPINE2","GATM","HSD3B1","INHA"),
                         "Early-BPGs"=c("IGFBP5","CDKN1C","JUN"),
                         "D-EPGs"=c("UPK3B","KRT19","GNG13","LGR5","IGFBP2","LHX9","ALDH1A2")) %>% lapply(function(x){
                intersect(x,rownames(seurat))})
```

## FeaturePlot{.tabset .tabset-fade}
### UMAP{.tabset .tabset-fade}

```{r, echo=FALSE, results='asis'}
reduction="umap"
res <- lapply(names(markers), function(i) {
  knitr::knit_child(
    '~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/Template/FeaturePlot.Rmd', envir = environment(), quiet = TRUE
  )
})
cat(unlist(res), sep = '\n')
```

```{r}
saveRDS(seurat,"~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/Final/1_batch_correct_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells.rds")
```