---
title: '2_annotation_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells'
author: "Ryuta Yokogawa"
output:
  html_document:
    number_sections: yes
    toc: true
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/Final")
```
data: 

Hs_in-vitro (NCLCN#261　d6c11, d6c56, d6c86, d6c117)
Hs_in-vivo (AC7w, AC9w, AC10w, YK11w, AC13w, AC16w)
res0.8


# Set up

```{r}
filename<-"2_annotation_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells"
orig.ident<-c("AC7w","AC9w","AC10w","YK11w","AC13w","AC16w", "c11", "c56","c86", "c117")
dataset<-c(rep("Hs_in-vivo",6), rep("Hs_in-vitro",4))
mapping<-"cr60GRCh38p12chrxmv1b1"
```

## Load libraries

```{r,message=FALSE,warning=FALSE}
suppressPackageStartupMessages({
  library(tidyverse)
  library(SeuratWrappers)
  library(patchwork)
  library(Seurat)
  library(Matrix)
  library(scales)
  library(data.table)
  library(gridExtra)
  library(knitr)
  library(scran)
  library(scater)
  library(pheatmap)
  library(gplots)
  library(RColorBrewer)
})
set.seed(0)
```

## Import data

```{r}
seurat <- readRDS("~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/Final/1_batch_correct_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells.rds")
```

## remove granulosa and N cluster
```{r}
seurat <-subset(seurat,subset=seurat_clusters%in%c("0","1","2","3","4","5","6","7","9","12"))
```

```{r}
theme_set(theme(text=element_text(size = 18),
                panel.background = element_rect(fill = "white",color="gray20"),
                panel.grid=element_line(color="gray92"),
                legend.key = element_rect(colour = NA, fill = NA)))
source("~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/core_functions.R")
```

```{r}
celltype_pal<-c(colorRampPalette(c("white","#008000"))(4)[4:3],
                colorRampPalette(c("white","#005080"))(4)[4:3],
                colorRampPalette(c("white","red"))(4)[4:2],
                "gold",
                "#b35900",
                "#a020f0"
                ) %>% 
  setNames(c("VEM1","VEM2","EM1","EM2","M1","M2","M3","PLL1","PLL2","ZPD"))
```

```{r}
orig_pal<-c("#f2a5a5","#F8766D","#FF62BC","#E76BF3","#39B600","#00BF7D","#00BFC4","#00B0F6","#9590FF","#5855e0") %>% 
  setNames(c("c11","c56","c86","c117","AC7w","AC9w","AC10w","YK11w","AC13w","AC16w"))
```

## Marker expression [annotationつける前にみる場合]

```{r,fig.width=6, fig.height=7}
markers<-intersect(c("NANOG","TFAP2C","UTF1","POU5F1","GTSF1","MEG3","PRAME","DAZL","SYCP3","DDX4","ANHX","ZGLP1","REC8","STRA8","SCP1","SYCP2","FIGLA","NOBOX","ZP3","MKI67","CCNA2"),rownames(seurat)) 
mat<-levels(seurat$seurat_clusters) %>% 
  lapply(function(y){
    if(y%in%seurat$seurat_clusters){
      if (sum(seurat$seurat_clusters==y)>1){
        seurat[["RNA"]]@data[markers,seurat$seurat_clusters==y] %>% 
          rowMeans()
        }else{
          seurat[["RNA"]]@data[markers,seurat$seurat_clusters==y]
        }
      }else{
          rep(NA,length(markers))
      }
  }) %>% do.call(cbind,.) %>% 
  as.data.frame() %>% 
  `colnames<-`(paste0(levels(seurat$seurat_clusters)))
mat_col <- data.frame(cluster=levels(seurat$seurat_clusters) %>% factor(levels(seurat$seurat_clusters)),
                      row.names = colnames(mat))
breaksList = c(seq(0, 1.99, by = 0.01),seq(2, 5, by = 0.05))
newnames <- lapply(
  rownames(mat),
  function(x) bquote(bolditalic(.(x))))

pheatmap(mat,cluster_rows = F,cluster_cols = FALSE, 
             color=colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(length(breaksList)),
             breaks = breaksList,
            #annotation_col_mat_col,
             show_colnames = T, show_rownames=T,
         labels_row = as.expression(newnames)
         #gaps_col = ncol(mat)-2
         )
```


# Analysis
## Annotation
```{r}
seurat@meta.data$cluster<-seurat@meta.data$seurat_clusters %>% 
  as.character()
use.switch<-function(x)
{
  lapply(x,function(y){
    switch(y,
           "5"="VEM1",
           "4"="VEM2",
           "2"="EM1",
           "9"="EM2",
           "0"="M1",
           "1"="M2",
           "3"="M3",
           "6"="PLL1",
           "7"="PLL2",
          "12"="ZPD",
           y
    )
  }) %>% unlist()
}
seurat@meta.data$cluster<-use.switch(seurat@meta.data$cluster) %>% 
  factor(levels=c("VEM1","VEM2","EM1","EM2","M1","M2","M3","PLL1","PLL2","ZPD"))
```

```{r,fig.width=12,fig.height=5,warning=FALSE}
p1<-DimPlot(object = seurat, reduction="umap", pt.size = 0.5,group.by="cluster",label=FALSE,label.size = 5)+
  scale_color_manual(values=celltype_pal)
p2<-DimPlot(object = seurat, reduction="umap", pt.size = 0.5, group.by = "orig.ident")
(p1+p2)
```

```{r}
table(seurat$orig.ident,seurat$cluster) %>% 
  addmargins()
```


## Filtering
skip 

## Distribution on UMAP

```{r,fig.width=25,fig.height=10}
dat<-seurat[["umap"]][[]] %>% as.data.frame()
dat$orig.ident<-seurat@meta.data$orig.ident
plts<-levels(dat$orig.ident) %>%
  lapply(function(x){
    ggplot(NULL)+
      geom_point(dat,mapping=aes(x=UMAP_1,y=UMAP_2),color="lightgrey",size=1)+
      geom_point(filter(dat,orig.ident==x),mapping=aes(x=UMAP_1,y=UMAP_2),color="red",size=1)+
      ggtitle(x)+
      theme(plot.title=element_text(size=30,hjust=0.5,vjust=1))+
      theme(axis.title=element_blank(),
                axis.text=element_blank(),
                axis.ticks=element_blank(),
                legend.position = "none")
  })

wrap_plots(plts, ncol = 5)&rd_theme()
```

## Marker expression [annotationつけた後にみる場合]

```{r}
markers <- c("NANOG","TFAP2C","UTF1","POU5F1","GTSF1","MEG3","PRAME","DAZL","SYCP3","DDX4","ANHX","ZGLP1","REC8","STRA8","SCP1","SYCP2","FIGLA","NOBOX","ZP3","MKI67","CCNA2") %>% intersect(rownames(seurat))
p1<-FeaturePlot(object = seurat, features = unlist(markers), min.cutoff = "q9", pt.size = 0.5, ncol=7, reduction="umap",label=FALSE)&rd_theme_italic()
ggsave(p1,filename=paste0(filename,"_markers.png"),width=25,height=11)
```

```{r,fig.width=6, fig.height=7}
markers<-intersect(c("NANOG","TFAP2C","UTF1","POU5F1","GTSF1","MEG3","PRAME","DAZL","SYCP3","DDX4","ANHX","ZGLP1","REC8","STRA8","SCP1","SYCP2","FIGLA","NOBOX","ZP3","MKI67","CCNA2"),rownames(seurat)) 
mat<-levels(seurat$cluster) %>% 
  lapply(function(y){
    if(y%in%seurat$cluster){
      if (sum(seurat$cluster==y)>1){
        seurat[["RNA"]]@data[markers,seurat$cluster==y] %>% 
          rowMeans()
        }else{
          seurat[["RNA"]]@data[markers,seurat$cluster==y]
        }
      }else{
          rep(NA,length(markers))
      }
  }) %>% do.call(cbind,.) %>% 
  as.data.frame() %>% 
  `colnames<-`(paste0(levels(seurat$cluster)))
mat_col <- data.frame(cluster=levels(seurat$cluster) %>% factor(levels(seurat$cluster)),
                      row.names = colnames(mat))
col_pal = list(cluster = celltype_pal)
breaksList = c(seq(0, 1.99, by = 0.01),seq(2, 5, by = 0.05))
newnames <- lapply(
  rownames(mat),
  function(x) bquote(bolditalic(.(x))))

pheatmap(mat,cluster_rows = F,cluster_cols = FALSE, 
             color=colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(length(breaksList)),
             breaks = breaksList,
             annotation_col=mat_col,
             annotation_colors = col_pal[1],
             show_colnames = F, show_rownames=T,
         labels_row = as.expression(newnames),
         #gaps_col = ncol(mat)-2
         )
```

## Marker expression [vivo vs vitro]

```{r,fig.width=6, fig.height=7}
seurat$method<-ifelse(seurat$orig.ident%in%c("c11","c56","c86","c117"),"in vitro","in vivo") %>% 
  factor(levels=c("in vivo","in vitro"))
for (i in levels(seurat$method)){
  seu<-subset(seurat,method==i)
  mat<-levels(seu$cluster) %>% 
  lapply(function(y){
    if(y%in%seu$cluster){
      if (sum(seu$cluster==y)>1){
        seu[["RNA"]]@data[markers,seu$cluster==y] %>% 
          rowMeans()
        }else{
          seu[["RNA"]]@data[markers,seu$cluster==y]
        }
      }else{
          rep(NA,length(markers))
      }
  }) %>% do.call(cbind,.) %>% 
  as.data.frame() %>% 
  `colnames<-`(paste0(levels(seu$cluster)))
mat_col <- data.frame(cluster=levels(seu$cluster) %>% factor(levels(seu$cluster)),
                      row.names = colnames(mat))
col_pal = list(cluster = celltype_pal)
breaksList = c(seq(0, 1.99, by = 0.01),seq(2, 5, by = 0.05))
newnames <- lapply(
  rownames(mat),
  function(x) bquote(bolditalic(.(x))))

pheatmap(mat,cluster_rows = F,cluster_cols = FALSE, 
             color=colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(length(breaksList)),
             breaks = breaksList,
             annotation_col=mat_col,
             annotation_colors = col_pal[1],
             show_colnames = F, show_rownames=T,
         labels_row = as.expression(newnames),
         #gaps_col = ncol(mat)-2,
         main=i)
}
```


```{r}
dat<-seurat[["RNA"]]@data[markers,] %>% 
  as.matrix() %>% 
  t() %>% 
  as.data.frame() %>% 
  rownames_to_column(var="cells") %>% 
  tidyr::pivot_longer(cols=-cells,names_to="genes",values_to="exp") %>% 
  transform(genes=factor(genes,levels=markers))
dat$cluster<-seurat@meta.data[dat$cells,"cluster"] %>% 
  factor(levels=levels(.) )
```

```{r,fig.width=14,fig.height=20}
p1<-ggplot(dat,aes(x=cluster,y=exp))+
  geom_violin(aes(fill=cluster),scale="width")+
  xlab("")+
  ylab("")+
  facet_wrap(genes~.,ncol=1, strip.position = "right")+
  theme_bw()+
  theme(panel.background = element_blank(),
        panel.grid = element_line(color = "white"), 
        strip.text.y = element_text(angle = 0,size=18, face="bold",hjust=0),
        axis.text.x = element_text(size=18,angle=45,hjust=1, face="bold"),
        strip.placement = "outside",
        strip.background = element_blank(),
        legend.position="none")+
  scale_fill_manual(values=celltype_pal)
p1
```

## Population of germ cells in each stage

```{r,fig.width=7,fig.height=5.5}
temp<-seurat@meta.data %>% 
  transform(cluster=factor(cluster,levels=levels(cluster))) %>% 
  group_by(orig.ident,cluster) %>% 
  summarise(count=n()) %>% 
  mutate(ratio=(count/sum(count)*100) %>% 
           round(digits=1) %>% 
           format(nsmall=1)) %>% 
  arrange(orig.ident, desc(cluster)) %>% 
  mutate(label_y = (cumsum(count) - 0.5 * count) / sum(count)) %>%
  transform(orig.ident = gsub("wpf"," wpf", orig.ident)) %>% 
  transform(orig.ident = gsub("_"," ",orig.ident) %>% factor(levels=c("c11","c56","c86","c117","AC7w","AC9w","AC10w","YK11w","AC13w","AC16w")))
ggplot(temp,aes(x=orig.ident,y=count,fill=cluster))+
  geom_bar(stat="identity",position="fill",color="black")+
  scale_y_continuous(labels=percent)+
  theme_bw(base_size = 15)+
  ylab("Percentage of germ cells")+
  xlab("")+
  scale_fill_manual(values=celltype_pal)+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(size=15,angle=45,hjust=1, color="black", face ="bold"),
        axis.text.y = element_text(size=15),
        axis.title = element_text(size=18,face="bold"),
        axis.line.x = element_line(size=1, color="black"),
        axis.line.y = element_line(size=1, color="black"),
        legend.text=element_text(size=15, color="black"),
        legend.title=element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.background = element_rect(fill='white'),
        strip.background = element_blank(),
        strip.text.x = element_blank()
)
```

```{r,fig.width=7,fig.height=5.5}
ggplot(temp,aes(x=orig.ident,y=count,fill=cluster))+
  geom_bar(stat="identity",position="fill",color="black")+
  geom_text(aes(label = count, y = label_y),size=3,hjust=0.5)+
  scale_y_continuous(labels=percent)+
  theme_bw(base_size = 15)+
  ylab("Percentage of germ cells")+
  xlab("")+
  scale_fill_manual(values=celltype_pal)+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(size=18,angle=45,hjust=1, color="black", face ="bold"),
        axis.text.y = element_text(size=15),
        axis.title = element_text(size=18,face="bold"),
        axis.line.x = element_line(size=1, color="black"),
        axis.line.y = element_line(size=1, color="black"),
        legend.text=element_text(size=15, color="black"),
        legend.title=element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.background = element_rect(fill='white'),
        strip.background = element_blank(),
        strip.text.x = element_blank()
)
```

## Population of germ cells in each cluster

```{r,fig.width=7,fig.height=5.5}
temp<-seurat@meta.data %>% 
  transform(cluster=factor(cluster,levels=levels(cluster))) %>% 
  group_by(orig.ident,cluster) %>% 
  summarise(count=n()) %>% 
  mutate(ratio=(count/sum(count)*100) %>% 
           round(digits=1) %>% 
           format(nsmall=1)) %>% 
  arrange(orig.ident, desc(orig.ident)) %>% 
  mutate(label_y = (cumsum(count) - 0.5 * count) / sum(count)) %>%
  transform(orig.ident = gsub("wpf"," wpf", orig.ident)) %>% 
  transform(orig.ident = gsub("_"," ",orig.ident) %>% factor(levels=c("c11","c56","c86","c117","AC7w","AC9w","AC10w","YK11w","AC13w","AC16w")))
ggplot(temp,aes(x=cluster,y=count,fill=orig.ident))+
  geom_bar(stat="identity",position="fill",color="black")+
  scale_y_continuous(labels=percent)+
  theme_bw(base_size = 15)+
  ylab("Percentage of germ cells")+
  xlab("")+
  scale_fill_manual(values=orig_pal)+
  theme_classic(base_size = 15)+
  theme(axis.text.x = element_text(size=15,angle=45,hjust=1, color="black", face ="bold"),
        axis.text.y = element_text(size=15),
        axis.title = element_text(size=18,face="bold"),
        axis.line.x = element_line(size=1, color="black"),
        axis.line.y = element_line(size=1, color="black"),
        legend.text=element_text(size=15, color="black"),
        legend.title=element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
        panel.background = element_rect(fill='white'),
        strip.background = element_blank(),
        strip.text.x = element_blank()
)
```

## Cell cycle (QuickGO meiotic cell cycle)

```{r}
cellcycle_pal<-c("#1F77B4","#FF7F0E","#2CA02C",
                "red") %>% 
  setNames(.,c("G1","S","G2M","Meiosis"))
```

```{r}
S<-cc.genes.updated.2019$s.genes
G2M<-cc.genes.updated.2019$g2m.genes
Meiosis<-fread("~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/Template/QuickGO_meiotic cell cycle.tsv",data.table = F)
Meiosis<-unique(Meiosis$SYMBOL)
cell_cycle<-data.frame(gene=c(S,G2M,Meiosis),
                       stage=c(rep("S",length(S)),rep("G2M",length(G2M)),rep("Meiosis",length(Meiosis))))
fun<-function(x){
  unique(x) %>% 
    length()
  }

a<-cell_cycle[cell_cycle$gene%in%cell_cycle$gene[duplicated(cell_cycle$gene)],] %>% 
  arrange(gene) %>% 
  group_by(gene) %>% 
  summarise(freq=fun(stage)) %>% 
  filter(freq>1)
a

cell_cycle<-filter(cell_cycle,duplicated(gene)==F) %>% 
  filter(gene%in%a$gene==FALSE)
```


```{r}
expressed_gene<-rownames(seurat)[rowSums(seurat[["RNA"]]@counts>=1)>2]
cellcycle<-filter(cell_cycle,gene%in%expressed_gene)
## cellcycle$gene<-fromHS(cellcycle$gene,"Mf",HsMf=TRUE)
table(cellcycle$stage)
```

```{r,fig.width=7,fig.height=7}
for (x in unique(cellcycle$stage)){
  gene<-cellcycle[cellcycle$stage==x,"gene"]
  mat<-seurat[["RNA"]]@data[gene,seurat$method=="in vivo"] %>% 
    as.matrix() %>% 
    t()
  mat<-cbind(mat,ref=rowMeans(mat))
  pheatmap(cor(mat),main=x)
} 
```

```{r}
CellCycleScoring. <- function(
  object,
  s.features,
  g2m.features,
  meiosis.features,
  ctrl = NULL,
  set.ident = FALSE,
  ...
) {
  name <- 'Cell.Cycle'
  features <- list('S' = s.features, 'G2M' = g2m.features, 'Meiosis' = meiosis.features)
  if (is.null(x = ctrl)) {
    ctrl <- min(vapply(X = features, FUN = length, FUN.VALUE = numeric(length = 1)))
  }
  object.cc <- AddModuleScore(
    object = object,
    features = features,
    name = name,
    ctrl = ctrl,
    ...
  )
  cc.columns <- grep(pattern = name, x = colnames(x = object.cc[[]]), value = TRUE)
  cc.scores <- object.cc[[cc.columns]]
  rm(object.cc)
  # CheckGC()
  assignments <- apply(
    X = cc.scores,
    MARGIN = 1,
    FUN = function(scores, null = 'G1') {
      if (all(scores < 0)) {
        return(null)
      } else {
        if (length(which(x = scores == max(scores))) > 1) {
          return('Undecided')
        } else {
          return(names(features)[which(x = scores == max(scores))])
        }
      }
    }
  )
  cc.scores <- merge(x = cc.scores, y = data.frame(assignments), by = 0)
  colnames(x = cc.scores) <- c('rownames', paste0(names(features),".Score"), 'Phase')
  rownames(x = cc.scores) <- cc.scores$rownames
  cc.scores <- cc.scores[, c(paste0(names(features),".Score"), 'Phase')]
  object[[colnames(x = cc.scores)]] <- cc.scores
  if (set.ident) {
    object[['old.ident']] <- Idents(object = object)
    Idents(object = object) <- 'Phase'
  }
  return(object)
}
```

```{r}
filtered_cellcycle<-cellcycle
seurat <- CellCycleScoring.(seurat, 
                            s.features = filtered_cellcycle$gene[filtered_cellcycle$stage%in%c("S")],
                            g2m.features = filtered_cellcycle$gene[filtered_cellcycle$stage%in%c("G2M")],
                            meiosis.features = filtered_cellcycle$gene[filtered_cellcycle$stage%in%c("Meiosis")])
seurat$Phase<-factor(seurat$Phase,levels=c("G1","S","G2M","Meiosis"))
```


```{r}
RidgePlot(seurat, features = c("PCNA", "TOP2A", "MCM6", "MKI67"), ncol = 2, group.by="Phase")&
  scale_fill_manual(values=cellcycle_pal)
```

```{r,fig.width=10,fig.height=8}
pdat<-seurat[["umap"]]@cell.embeddings %>% 
  as.data.frame() %>% 
  cbind(seurat@meta.data)
pdat<-pdat[order(seurat$cluster),]
p1<-ggplot(pdat,aes(x=UMAP_1,y=UMAP_2,color=Phase))+
  geom_point(size=1.5)+
  scale_color_manual(values=cellcycle_pal)+
  rd_theme(legend.position = "right")+
  guides(color = guide_legend(override.aes = list(size = 5)))+
  theme(axis.line = element_line(colour = 'black', size = 1))
p1

# pdf(paste0(filename,"_rough_Tirosh_cellcycle_UMAP_simple_legend.pdf"), width = 10, height = 8)
# print(p1)#メインのグラフ
# dev.off()
```

```{r,fig.width=8,fig.height=8}
pdat<-seurat[["umap"]]@cell.embeddings %>% 
  as.data.frame() %>% 
  cbind(seurat@meta.data)
pdat<-pdat[order(seurat$cluster),]
p1<-ggplot(pdat,aes(x=UMAP_1,y=UMAP_2,color=Phase))+
  geom_point(size=1.5,show.legend = F)+
  scale_color_manual(values=cellcycle_pal)+
  rd_theme(legend.position = "right")+
  guides(color = guide_legend(override.aes = list(size = 5)))+
  theme(axis.line = element_line(colour = 'black', size = 1))
p1

# pdf(paste0(filename,"_rough_Tirosh_cellcycle_UMAP_simple.pdf"), width = 8, height = 8)
# print(p1)#メインのグラフ
# dev.off()
```

### Population of germ cells in each stage

```{r}
mytheme<-function(){
  theme_minimal()+
  theme(axis.text.x = element_text(size=25, color="black",face="bold",angle=90,hjust=1,vjust=0.5),
        axis.text.y = element_text(size=18, color="black",face="bold"),
        legend.text=element_text(size=17, color="black"),
        legend.title=element_text(size=19, color="black"),
        axis.line.x = element_line(size=1.2, color="black"),
        axis.line.y = element_line(size=1.2, color="black"),
        strip.text = element_text(size=30, face="bold",color="black"),
        axis.title = element_text(size=22,face="bold"),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(), 
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.ticks=element_line(size=0.8),
        axis.ticks.length.y=unit(0.2,units="cm"),
        strip.background = element_blank()
        )
}
```

```{r,fig.width=8,fig.height=5.5}
seurat$sample<-seurat$orig.ident
temp<-seurat@meta.data %>% 
  group_by(sample,Phase) %>% 
  summarise(count=n()) %>% 
  mutate(ratio=(count/sum(count)*100) %>% 
           round(digits=1) %>% 
           format(nsmall=1)) %>% 
  arrange(sample, desc(Phase)) %>% 
  mutate(label_y = (cumsum(count) - 0.5 * count) / sum(count))

```

```{r,fig.width=6,fig.height=5}
p1<-ggplot(temp,aes(x=sample,y=count,fill=Phase))+
  geom_bar(stat="identity",position="fill",color="black",size=0.8)+
  #geom_text(aes(label = count, y = label_y),size=3,hjust=0.5)+
  scale_y_continuous(labels=percent)+
  theme_bw(base_size = 15)+
  ylab("Percentage of germ cells")+
  xlab("")+
  scale_fill_manual(values=cellcycle_pal)+
  mytheme()
p1
# pdf(paste0(filename,"_rough_Tirosh_cellcycle_simple.pdf"),width=6, height=5)
# p1
# dev.off()
```

```{r,fig.width=8,fig.height=5.5}
seurat$sample<-seurat$cluster
temp<-seurat@meta.data %>% 
  group_by(sample,Phase) %>% 
  summarise(count=n()) %>% 
  mutate(ratio=(count/sum(count)*100) %>% 
           round(digits=1) %>% 
           format(nsmall=1)) %>% 
  arrange(sample, desc(Phase)) %>% 
  mutate(label_y = (cumsum(count) - 0.5 * count) / sum(count))
```

```{r,fig.width=8,fig.height=5.5}
ggplot(temp,aes(x=sample,y=count,fill=Phase))+
  geom_bar(stat="identity",position="fill",color="black")+
  geom_text(aes(label = count, y = label_y),size=3,hjust=0.5)+
  scale_y_continuous(labels=percent)+
  theme_bw(base_size = 15)+
  ylab("Percentage of germ cells")+
  xlab("")+
  scale_fill_manual(values=cellcycle_pal)+
  mytheme()
```


# Save

```{r}
saveRDS(seurat,"~/Library/CloudStorage/OneDrive-KyotoUniversity/10xanalysis/RMD for analysis/Murase_paper/Final/2_annotation_vivoACYK_c11_56_86_117_res0.8_5000HVGs_exp2in5cells.rds")
```
